The importance of measurement uncertainty in ecological management

### 2018-02-01 manuscripts/manuscript.Rmd
manuscript, also separate figure files

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE,  dev="cairo_pdf", cache = TRUE)
library(tidyverse)
library(gridExtra)
```

>>>>

```{r libraries, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE,  dev="cairo_pdf", cache = FALSE)
library(tidyverse)
library(gridExtra)
```
